### 2021-05-24 paper/sections/backend/__latexindent_temp.tex

Audioguide per il beacon indicato
\begin{lstlisting}[ language=SQL,
                    deletekeywords={IDENTITY},
                    deletekeywords={[2]INT},
                    morekeywords={clustered},
                    framesep=8pt,
                    xleftmargin=40pt,
                    framexleftmargin=40pt,
                    frame=tb,
                    framerule=0pt ]
SELECT * FROM audioguides INNER JOIN rooms ON audioguides.room_id = rooms.id WHERE beacon_id={beacon_code}
\end{lstlisting}
Articoli di una stanza
\begin{lstlisting}[ language=SQL,
                    deletekeywords={IDENTITY},
                    deletekeywords={[2]INT},
                    morekeywords={clustered},
                    framesep=8pt,
                    xleftmargin=40pt,
                    framexleftmargin=40pt,
                    frame=tb,
                    framerule=0pt ]
SELECT employees.name, employees.surname, articles.id, articles.title, articles.body
FROM articles
INNER JOIN room_articles ON room_articles.room_id = {room_id}
INNER JOIN employees ON articles.employee_id = employees.id
\end{lstlisting}
Aritcoli scritti da un autore (ricerca per nome)
\begin{lstlisting}[ language=SQL,
                    deletekeywords={IDENTITY},
                    deletekeywords={[2]INT},
                    morekeywords={clustered},
                    framesep=8pt,
                    xleftmargin=40pt,
                    framexleftmargin=40pt,
                    frame=tb,
                    framerule=0pt ]
                    elect
                    employees.name, employees.surname,
                    articles.id, articles.title, articles.body
                    from articles
                    inner join employees on articles.employee_id = employees.id
                    where employees.name LIKE ?
\end{lstlisting}