### 2021-05-31 paper/sections/abstract.tex
add external links

The following work aims at analysing and designing the prototype of a mobile application, available both on iOS and Android, intended for use by an eighteenth-century villa that wants to reorganise its audioguide mechanism so that visitors can use their personal devices.
The general requirements for such a service will be studied, with particular attention to the basic functionalities that the application must offer; the characteristics of the network infrastructure will be evaluated, with a focus to the devices that allow to detect the position of the visitor. Furthermore, the administration panel used by the staff to access the actual visitor count and to close or open access to the rooms will be analysed. The tools made available by the various programming languages, frameworks and libraries that have allowed the development of some of the functionalities will be presented. A part will also be devoted to security, a fundamental aspect of any application. Finally, the results achieved and possible improvements to be made in the future will be analysed in order to obtain a quality product.\\\\
Il presente lavoro mira ad analizzare e progettare il prototipo di un'applicazione mobile, disponibile sia su iOS che su Android, destinata all'uso in una villa storica risalente al diciottesimo secolo. Lo scopo è quello di riorganizzare il meccanismo di audioguide in modo che i visitatori possano utilizzare i loro dispositivi personali.
Verranno studiati i requisiti generali di tale servizio, con particolare attenzione alle funzionalità di base che l'applicazione deve offrire; saranno valutate le caratteristiche dell'infrastruttura di rete, con particolare attenzione ai dispositivi che permettono di rilevare la posizione del visitatore. A questo farà seguito l'analisi del pannello di amministrazione utilizzato dal personale per accedere al conteggio effettivo dei visitatori e per chiudere o aprire l'accesso alle stanze. 
Verranno presentati gli strumenti messi a disposizione dai vari linguaggi di programmazione, framework e librerie che hanno permesso lo sviluppo di alcune delle funzionalità. Una parte sarà anche dedicata alla sicurezza, un aspetto fondamentale di qualsiasi applicazione. Infine, verranno analizzati i risultati raggiunti e i possibili miglioramenti da apportare in futuro per ottenere un prodotto di qualità.